---
title: "Treatment characterization"
runtime: shiny
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    theme : yeti
    vertical_layout: scroll
---

```{r global_packages}
library(flexdashboard)
library(shiny)
library(PathwayVisualizer)
library(dplyr)
```


Usage Patterns
============================

Column
----------------------------

### Usage patterns of the treatment 1

```{r, echo=FALSE}
PathwayVisualizer::plot1(p1_data,
                         type = 'area')

```

### Usage patterns of the treatment 2

```{r, echo=FALSE}

PathwayVisualizer::plot1(p1_data,
                         type = 'line')

```

Column
----------------------------

### Treatment Iteration Heatmap

```{r, echo=FALSE}

PathwayVisualizer::plot2(p2_data,
                         minimumCellCount)


```


Treatment Pathway
============================

Column {data-width=650}
----------------------------

### Treatment Pathway

```{r, echo=FALSE}

PathwayVisualizer::plot3(p3_data)

```

Column {data-width=350}
----------------------------

### Pathway raw data 

```{r, echo=FALSE,fig.keep='all'}

pathways <- p3_data$pathways
knitr::kable(pathways)

```

Event Onset Timing
================================

Column {.tabset .tabset-fade }
--------------------------------

### Regression Plot

```{r, echo=FALSE,fig.keep='all'}

PathwayVisualizer::plot4(p4_data,type = 'regression')

```

### Incidence Histogram

```{r, echo=FALSE}

PathwayVisualizer::plot4(p4_data,type = 'histogram')

```

### Onset Date

```{r, echo=FALSE,fig.keep='all'}

PathwayVisualizer::plot5(p5_data)

```   

About
================================

Copyright 2020 Observational Health Data Sciences and Informatics

This file is part of PathwayVisualizer

Licensed under the Apache License, Version 2.0 (the "License");
you may not use this file except in compliance with the License.
You may obtain a copy of the License at

http://www.apache.org/licenses/LICENSE-2.0

Unless required by applicable law or agreed to in writing, software
distributed under the License is distributed on an "AS IS" BASIS,
WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
See the License for the specific language governing permissions and
limitations under the License.
